Model

### 2019-11-13 stats/model.Rmd
first draft prior model
prior model update

      display(subjects)

      var subj_age = subjectData[0].age
      var subjectPrior = sampleSub(subj_age)

@@

prior_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, prior_params , sep='\n'),
  data = list(data = prior_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "MCMC", samples = 10000, burn = 5000, verbose = T)
)

prior <- prior_model%>%
  mutate(value = unlist(value))%>%
  filter(Chain !=2)

@@

@@

```{r}
novel_bm <- readRDS("../saves/novelty_model.rds")
summary(novel_bm)
```

>>>>

      var subj_age = subjectData[0].age

      var subjectPrior = sampleSub(subj_age)

      display(subjectPrior)

@@

prior_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, prior_params , sep='\n'),
  data = list(data = prior_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 1,
  inference_opts = list(method = "MCMC", samples = 1, burn = 1, verbose = T)
)

saveRDS(prior_model, "../saves/prior_model.rds")

prior <- prior_model%>%
  mutate(value = unlist(value))

@@

#### Visualizing parameters

@@

#### Comparison to brm models

# same model as webppl model  implemented in brms

novel_bm <- brm(correct ~ age + (1 | subid), 
          data = prior_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 20000)

saveRDS(novel_bm, "../saves/novelty_model_brm.rds")
```

```{r}
# brm model from last chunk
novel_bm <- readRDS("../saves/novelty_model_brm.rds")

brm_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
  select(term,Estimate)%>%
  spread(term, Estimate)

brm_plot <- tibble(
  age = prior_data$age,
  y = plogis(brm_params$Intercept + brm_params$age * age),
  model = "brm"
)

#brm model with additional random intercept and slope for item
novel_bm_full <- readRDS("../saves/novelty_model.rds")

brm_full_params <- as_tibble(fixef(novel_bm_full), rownames = "term")%>%
  select(term,Estimate)%>%
  spread(term, Estimate)

brm_full_plot <- tibble(
  age = prior_data$age,
  y = plogis(brm_full_params$Intercept + brm_full_params$age_num * age),
  model = "brm_full"
)

# webppl model
webppl_plot <- tibble(
  age = prior_data$age,
  y = plogis(prior_summary%>%filter(Parameter == "intercept")%>%pull(param_map) + prior_summary%>%filter(Parameter == "slope")%>%pull(param_map) * age),
  model = "webppl"
)

prior_comp_plot <- bind_rows(
  brm_plot,
  webppl_plot,
  brm_full_plot

)
```

```{r}
ggplot(prior_comp_plot, aes(x = age, y = y, col = model))+
  geom_line()+
  ylim(0,1)+
  theme_few()+
  scale_color_ptol()
```
